Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
some fixes

\textbf{\textit{Security refactorings harm the maintainability of open-source software.}}
\Luis{Nao uses numeros no inico da frase. --> We found that 40.2\% of the security refactorings}

In particular, 40.2\% of the security refactoring have a negative impact on the
maintainability of open-source software, Figure~\ref{fig:secvsreg}. This raises
a new tradeoff when developers need to fix vulnerabilities on their projects
because they might be affecting the software maintainability or even introducing
new vulnerabilities. This study exhibits evidence that developers may have to
reduce maintainability for the sake of safety. We understand that developers
should be able to produce secure code without affecting the maintainability of
their projects. But there are still some concerns that need to be addressed:
\begin{itemize}
	\item \textbf{Security Frameworks} need to be secure and user-friendly~\cite{5287006, 7676144}. Unfortunately,
	there are several vulnerabilities that stay undisclosed. Thus, developers should not
	trust them blindly and check defaults.
	\item \textbf{Documentation} of software should provide developers with the best practices to implement safe and maintainable software. Unmaintainable code is difficult to test, analyze and re-use.
	\item \textbf{Proper Authorization Mechanisms} should be designed and implemented. This is
	one of the most complex security features to implement. Some mechanisms might assist authorization maintenance in long run, such as the combination of \texttt{HTTP} filters with \texttt{Spring Security} annotations.
	\item \textbf{Deprecated code} should be avoided by developers. They should integrate tools such as BCH on their projects CI/CD pipelines to help them be more aware of the maintainability of their code and issues (e.g., dead and duplicated code).
	\item\textbf{Programming Languages} should provide new mechanisms to easily implement security patterns without endangering maintainability.

@@

\Luis{Better Code Hub -> BCH}
The maintainability formula was inferred based on the reports of the Better Code Hub.
The high amount of different projects and backgrounds may require different maintainability
standards. However, BCH does have a representative benchmark of closed and open-source
software projects that is under the calculation of the thresholds used in the computation
of each maintainability guideline (Table~\ref{tab:guidelines})~\cite{Visser:2016:OREILLY,
Baggen2012}.

@@

Baseline commits are retrieved randomly by selecting one commit from the same
project of a given security refactoring. This approach softens the differences
that may result from the characteristics of each project. However,
maintainability still may be affected by the developers experience, coding
style and software contribution polices which it is not evaluated in this
study. Furthermore, this evaluation considers that 607 regular commits are
enough to alleviate random irregularities in the maintainability differences of
the baseline.

\Luis{maintainability still may be affected -> maintainability may sitll be affected}

@@

\Luis{A primeira threat que falas é que os resultados podem nao generalizar
para software fechado. Eu acho que deviamos ser mais diretos. Para alem disso
tirava o "In contrast to the BCH benchmark,"}

In contrast to the BCH benchmark, this study uses a dataset that only covers
open-source software to perform the maintainability evaluation. However, BCH
thresholds are calculated from a set of both open and closed software.
Different programming languages may require different coding practices to
address software safety. The dataset comprises more commits in C and PHP, i.e.,
the dataset may not be properly representative of the population regarding to
programming languages.

@@

\Luis{pode ser uma cena só minha mas acho que fica melhor em vez de comecar
fraseds com "And," usar outros conetores tipo "Besides," "In addition,", etc. œ}

@@

\Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
diferenca é que estamos a estudar maintainability issues noutro contexto.}

@@

\Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}

@@

\Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

@@

\Luis{many directions such as -> many directions:}
\Luis{evaluate the impact of programming languages of the
maintainability of each refactoring pattern; - > evaluate the impact of each refactoring pattern on the maintainbility of each  }

As future work, this study may be extended in many directions such as analyze which guidelines are
more likely to affect security refactorings; evaluate the impact of programming languages of the
maintainability of each refactoring pattern; investigate if there is any correlation between
software maintainability and projects popularity; expand our methodology with other software quality
properties; validate these findings with closed or private software; and, expand this analysis
to other quality standards.

>>>>

\textbf{\textit{Security refactorings harm the maintainability of open-source software.}}

We found that 40.2\% of the security refactoring have a negative impact on the
maintainability of open-source software, Figure~\ref{fig:secvsreg}. This raises
a new tradeoff when developers need to fix vulnerabilities on their projects
because they might be affecting the software maintainability or even introducing
new vulnerabilities. This study exhibits evidence that developers may have to
reduce maintainability for the sake of safety. We understand that developers
should be able to produce secure code without affecting the maintainability of
their projects. But there are still some concerns that need to be addressed:
\begin{itemize}
	\item \textbf{Security Frameworks} need to be secure and user-friendly~\cite{5287006, 7676144}. Unfortunately,
	there are several vulnerabilities that stay undisclosed. Thus, developers should not
	trust them blindly and check defaults.
	\item \textbf{Documentation} of software should provide developers with the best practices to implement safe and maintainable software. Unmaintainable code is difficult to test, analyze and re-use.
	\item \textbf{Proper Authorization Mechanisms} should be designed and implemented. This is
	one of the most complex security features to implement. Some mechanisms might assist authorization maintenance in long run, such as the combination of \texttt{HTTP} filters with \texttt{Spring Security} annotations.
	\item \textbf{Deprecated code} should be avoided by developers. They should integrate tools such as BCH on their projects CI/CD pipelines to help them be more aware of the maintainability of their code and issues (e.g., dead and duplicated code).
	\item\textbf{Programming Languages} should provide new mechanisms to easily implement security patterns without endangering maintainability.

@@

The maintainability formula was inferred based on the BCH's reports.
The high amount of different projects and backgrounds may require different maintainability
standards. However, BCH does have a representative benchmark of closed and open-source
software projects that is under the calculation of the thresholds used in the computation
of each maintainability guideline (Table~\ref{tab:guidelines})~\cite{Visser:2016:OREILLY,
Baggen2012}.

@@

Baseline commits are retrieved randomly by selecting one commit from the same
project of a given security refactoring. This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may sitll be affected by the developers experience, coding
style and software contribution polices which it is not evaluated in this
study. Furthermore, this evaluation considers that 607 regular commits are
enough to alleviate random irregularities in the maintainability differences of
the baseline.

@@

% \Luis{A primeira threat que falas é que os resultados podem nao generalizar
% para software fechado. Eu acho que deviamos ser mais diretos.}\Sof{Diretos como?}

This study uses a dataset that only covers
open-source software to perform the maintainability evaluation. However, BCH
thresholds are calculated from a set of both open and closed software.
Different programming languages may require different coding practices to
address software safety. The dataset comprises more commits in C and PHP, i.e.,
the dataset may not be properly representative of the population regarding to programming languages.

@@

% \Luis{pode ser uma cena só minha mas acho que fica melhor em vez de comecar
% fraseds com "And," usar outros conetores tipo "Besides," "In addition,", etc. œ}

@@

% \Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
% Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
% diferenca é que estamos a estudar maintainability issues noutro contexto.}

@@

% \Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}

@@

% \Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

@@

As future work, this study may be extended in many directions: analyze which guidelines are
more likely to affect security refactorings; evaluate the impact of each refactoring pattern on software maintainbility; investigate if there is any correlation between
software maintainability and projects popularity; expand our methodology with other software quality
properties; validate these findings with closed or private software; and, expand this analysis
to other quality standards.
